\chapter{State of art}

Main activity: Paper reading

Introduction to Sentiment Analysis.
Relevant International Workshop found: SemEval
→ Datasets repositories: Twitter as corpus, Amazon products reviews…
→ Dataset labeling: CrowdFlower, Amazon Mechanical Turk.
→ Word embedding: Word2vec, GloVe.
→ Text classification features: N-grams based on Sentiment lexicon…
→ Learning Methods: Supervised, Unsupervised, Distant…
→ Deep Learning techniques: Convolutional NN, Recurrent NN, Deep Autoencoders…
→ Classifiers: “Bag of Words”, Naive Bayes, Logistic Regression, SVM, NN, Clustering…
→ Accuracy evaluation: Precision, Recall, F1-Score, Cross-validation…
→ Trends: Best scoring teams used Deep Learning techniques.

Differences between Sentiment and Emotion Analysis

SemEval works on sentiment analysis, which focuses on binary or multiclass classification, being Positive, Neutral and Negative the most common one.
This means:
 None of the SemEval preprocessed datasets are valid for me. (Raw data may work for manual annotation)
 The need of procedure adaptation to fit my research domain.
E.g. Use Emotion lexicon, such as EmoLex or LIWC, instead of  those related to Sentiment.
Need to focus the research on discover word features that help to classify anger in texts.
E.g. Heavy Punctuation, Quotation Marks, Emoticons; Unigrams, among others.

Next week work: Deep reading and prepare a Playground with small sample data.

Read fundamental theory about classifiers such as SVN, Bayesian, KNN, Decision Tree.
Urge test what has been learned in order to set the basic knowledge.
→ Download and test WEKA’s basic functionalities for educational and research purpose. (Includes a No-Code-GUI, which makes it user friendly for initial testings)
→ Use scikit-learn for following iterations of the classifier (More modern algorithms, better memory management, Python development environment...)
Further reading about Emotion classification techniques and investigate about repressed anger in English texts. 
Multiclass angry classification?

Future work: Deep Learning

Depending on the generated dataset (size and labeled/unlabeled) the project could opt for a DL based classifier.
Could score better results in the benchmarking.
→ To gather large amount of data for each class is compulsory solve the overfitting problem. (Detection and prevention by using Cross-validation)
→ If the dataset is not completely labeled weakly (distant) supervised learning could be applied.
→ Theano and Keras have proved a DL frameworks to perform well.


\input{contents/3-state-of-art/1-algorithms}